A planetary collision afterglow and transit of the resultant debris cloud

### 2023-10-12 src/tex/ms.tex
[showyourwork] overleaf sync

        \hline
    \end{tabular}
    \footnotetext[1]{Gaia EDR3 \cite{Brown21}, coordinates are J2000 at epoch 2000.0.}
    \footnotetext[2]{\cite{BailerJones21}}
    \footnotetext[3]{2MASS \cite{Cutri03}, $J$ is an upper limit and $H$ and $K_s$ are flagged as contaminated.}
    \footnotetext[4]{APASS \cite{2015AAS...22533616H}, this photometry includes a nearby star.}
    \footnotetext[5]{Estimated from an SED fit fixed to Gaia properties.}
    \footnotetext[6]{Estimated using mean stellar properties \cite{2013ApJS..208....9P}.}
    \footnotetext[7]{Estimated using rotation period.}

@@

\begin{figure}
    \centering
\includegraphics[width=1\textwidth]{figures/blueing.pdf}
    \caption{Blueing of the $B-V$ colour during dimming.
    %
    Points show AAVSO data, and lines show models.
    %
    The dashed line is a line of $A_\lambda/A_V$ for the value shown in the legend in each panel, and the solid line is a model that includes an underlying scattered light component with $s=7.5$\% of the stellar flux.
    %
    Error bars are shown at $1\sigma$ confidence.
}
    \label{fig:blueing}
    \script{blueing.py}
\end{figure}

@@

\begin{figure}
    \centering
\includegraphics[width=1\textwidth]{figures/asassn-21qj-cartoon.pdf}
    \caption{Sketch of ASASSN-21qj hypothesis.}
    % \caption{\textbf{Sketch of the hypothesis for the observations seen towards ASASSN-21qj.}
    % %
    % At $t=0$, the collision occurs, producing a cloud of debris that expands and cools.
    % %
    % Material close to the remnant is heated by its luminosity, generating the 1000\,K infrared emission.
    % %
    % Around 1000 days later, the expanding cloud crosses the line of sight between the star and the Earth, generating the optical light curve.}
    \label{fig:hypothesis}
\end{figure}

@@

\bmhead{Availability of data and materials}
The data sets generated and analysed during the current study are available in the Zenodo repository \url{https://zenodo.org/record/8344755}.

\bmhead{Code availability} 
All the code for the analysis and the generation of all the figures  are available in a showyourwork \citep{Luger2021} reproducible framework available as a git repository on github: \url{https://github.com/mkenworthy/ASASSN-21qj-debris/}.
%
The source code and documentation for the SWIFT open-source simulation code is available from \url{www.swiftsim.com}.

>>>>

        \hline
    \end{tabular}
    \footnotetext[1]{Gaia DR3 \cite{Brown2023}, coordinates are J2000 at epoch 2000.0.}
    \footnotetext[2]{\cite{BailerJones21}}
    \footnotetext[3]{2MASS \cite{Cutri03}, $J$ is an upper limit and $H$ and $K_s$ are flagged as contaminated.}
    \footnotetext[4]{APASS \cite{2015AAS...22533616H}, this photometry includes a nearby star.}
    \footnotetext[5]{Estimated from an SED fit fixed to Gaia properties.}
    \footnotetext[6]{Estimated using mean stellar properties \cite{2013ApJS..208....9P}.}
    \footnotetext[7]{Estimated using rotation period.}

@@

\begin{figure}
    \centering
\includegraphics[width=1\textwidth]{figures/blueing.pdf}
    \caption{\textbf{Blueing of the $B-V$ color during dimming.}
    %
    Points show AAVSO data, and lines show models.
    %
    {\bf a},The $V$ magnitude versus $B-V$ color and {\bf b}, the  $V$ magnitude versus $V-I$ color.
    %
    The dashed line is a line of $A_\lambda/A_V$ for the value shown in the legend and the solid line is a model that includes an underlying scattered-light component with $s=7.5$\% of the stellar flux.
    %
    Error bars are shown at $1\sigma$ confidence.
}
    \label{fig:blueing}
    \script{blueing.py}
\end{figure}

@@

\begin{figure}
    \centering
\includegraphics[width=1\textwidth]{figures/asassn-21qj-cartoon.pdf}
    \caption{\textbf{Sketch of the hypothesis for the observations seen towards ASASSN-21qj.}
    %
    At $t=0$, the collision occurs, producing a cloud of debris that expands and cools.
    %
    Material close to the remnant is heated by its luminosity, generating the 1000\,K infrared emission.
    %
    Around 1000 days later, the expanding cloud crosses the line of sight between the star and the Earth, generating the optical light curve.}
    \label{fig:hypothesis}
\end{figure}

@@

\bmhead{Availability of data and materials}
The data sets generated and analysed during the current study are available in the Zenodo repository \url{https://doi.org/10.5281/zenodo.8344755}.

\bmhead{Code availability} 
All the code for the analysis and the generation of all the figures  are available in a showyourwork \citep{Luger2021} reproducible framework available as a git repository on github: \url{https://github.com/mkenworthy/ASASSN-21qj-collision/}.
%
The source code and documentation for the SWIFT open-source simulation code is available from \url{www.swiftsim.com}.
